30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-14 paper.tex
back to peer-to-peer!

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
	There are quite a few distributed anonymous communication networks such as Tor, yet when it comes to decentralized anonymous systems the numbers are rather small and certain problems arise. In this technical report we explain how Tor works and which attacks are possible and which vulnerabilities currently exist in Tor. After that, we talk about why would like to decentralize peer-to-peer networks, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized. Finally, we provide a table in where we compare these projects against each other, which will also be public available on the Github page mention in this report.
\end{abstract}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
	There are quite a few distributed anonymous communication networks such as Tor, yet when it comes to decentralized anonymous systems the numbers are rather small and certain problems arise. In this technical report we explain how Tor works and which attacks are possible and which vulnerabilities currently exist in Tor. After that, we talk about why would like to decentralize these peer-to-peer networks, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized. Finally, we provide a table in where we compare these projects against each other, which will also be public available on the Github page mention in this report.
\end{abstract}
